\documentclass[11pt,a4paper,sans]{moderncv}
% moderncv themes
\moderncvstyle{banking}
% 'casual' (default), 'classic', 'oldstylef', 'banking'
\moderncvcolor{green}
%\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}
% if you are not using xelatex ou lualatex, replace by the encoding you are using

\usepackage{fontawesome5}
% adjust the page margins
\usepackage[scale=0.9]{geometry}

%\setlength{\hintscolumnwidth}{3cm}
% if you want to change the width of the column with the dates


%------------ personal data ----------
\name{Roozbeh}{Sharifnasab}
\title{}
%\insti{Shahid Beheshti University}
\insti{}
%\address{Address: Taban St}{Valiasr Ave}{Tehran, Iran}
%\phone[mobile]{+98 937 236 3864}
\email{rsharifnasab@gmail.com}
\homepage{rsharifnasab.ir}
\extrainfo{
    \homepagesymbol\httplink{linkedin.com/in/rsharifnasab}
    \homepagesymbol\httplink{github.com/rsharifnasab}
}
\begin{document}
\hypersetup{
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\urlstyle{same}
\noindent
\makecvtitle

\vspace{-0.5em}

%------------------ EDUCATION --------------
\vspace{-0.4em}
\section{Education}

%%%%%%%%%%%%%% MSC %%%%%%%%%%%
\cventry{}{Shahid Beheshti University}
{M.Sc (Computer Software)}{2022-2024 (Expected)}{}{}
\cvlistitem{~\textbf{Average: 18.22/20 (GPA: 3.77/4)}}
\cvlistitem{~Selected courses:}
%\hskip
%\begin{adjustwidth}{4mm}{}
\small{
	\begin{tabular}
		{l@{\hskip 5mm}l@{\hskip 5mm}l}
		~~~~~~Seminar (19.2/20)   &    Advanced Software Testing, Debugging and Repair (19/20) \\
		~~~~~~Software Architecture (19.39/20)  & Complex Dynamic Networks (19.54/20) \\
		% ~~~~~~Advanced Computer Networks (18.3/20)  &   \\
	\end{tabular}
	\medskip
	%\end{adjustwidth}
} % small

\vspace{-0.2em}
\cvlistitem{Approved thesis proposal: \textbf{Code Reviewer Recommendation with Graph-based approach}}
\cvlistitem{Under supervision of Dr. Aliakbary}

%%%%%%%%%%%%% B.SC
\vspace{0.6em}

\cventry{}{Shahid Beheshti University}
{B.Sc (Computer Engineering)}{2018-2022}{}{}
\cvlistitem{~\textbf{Average: 17.7/20 (GPA: 3.71/4)}}
\cvlistitem{~Selected courses:}
%\hskip
%\begin{adjustwidth}{4mm}{}
\small{
	\begin{tabular}
		{l@{\hskip 5mm}l@{\hskip 5mm}l}
		~~~~~~Fundamentals of Programming (20/20) & Advanced Programming (20/20) & Principles of Compiler Design (17/20) \\
		~~~~~~Operating Systems (18.3/20) & Internet Engineering (20/20) &  Computer Networks (20/20) \\
		~~~~~~Information Retrieval \& Web search (18.4/20) & System Analysis \& Design (19/20) & B.Sc Project (20/20)

	\end{tabular}
	\medskip
	%\end{adjustwidth}
} % small

\vspace{-0.5em}
\cvlistitem{B.Sc Project: A utility for TAs which helps them judge students' codes more flexibly}
\cvlistitem{Under supervision of Dr. Vahidi}

%%%%%%%%%%%%%%% DIPLOMA

\vspace{0.6em}
\cventry{}{Allameh Helli 3 High School}
{Diploma (Mathematics \& Engineering)}{2014-2018}{}{}
\cvlistitem{~Average: 19.72/20}
\cvlistitem{~Affiliated with the National Organization for the Development of Exceptional Talents (NODET).}


% ---------------- TA -------------
\vspace{-1em}

\section{Teaching Assistant}

\vspace{3pt}
\begin{itemize}


\item{\cventry{}{Shahid Beheshti University}{Software Architecture (x1)}{Fall 2023}{}{
		\begin{itemize}
			\item {Under the supervision of \textbf{Dr. Aliakbary}}
			\item {Grading submissions}
		\end{itemize}
}}


\item{\cventry{}{Shahid Beheshti University}{Operating Systems (x5)}{Since Fall 2021}{}{
\begin{itemize}
\item {Under the supervision of \textbf{Prof. Moghadam}}
\item {Head TA, Develop assignments, Grading submissions}
\end{itemize}
}}


\item{\cventry{}{Shahid Beheshti University}{Introduction to programming (x6) }{Since Fall 2019}{}{
\begin{itemize}
\item {Under the supervision of \textbf{Dr. Aliakbary} and \textbf{Parham Alvani}}
\item {Head TA, Develop assignments, Hold TA classes, Grading submissions}
\end{itemize}
}}

\item{\cventry{}{Shahid Beheshti University}{Advanced programming (x9)}{Since  Spring 2020}{}{
\begin{itemize}
\item Under the supervision of \textbf{Dr. Aliakbary} and \textbf{Dr.Vahidi} and \textbf{Dr. Mosharraf}
\item {Head TA,  Develop assignments, Hold TA classes, Grading submissions}
\end{itemize}
}}

\item{\cventry{}{Shahid Beheshti University}{Internet Engineering (x1)}{ Spring 2021}{}{
		\begin{itemize}
			\item Under the supervision of \textbf{Parham Alvani}
			\item {Head TA, Develop assignments, Hold TA classes, Grading submissions}
		\end{itemize}
}}


\item{\cventry{}{Sharif University of Technology}{ Principles of Compiler Design (x2)}{Spring 2022}{}{
		\begin{itemize}
			\item Under the supervision of \textbf{Dr. Mohammad Reza Bahrami}
			\item Project automatic judgment
		\end{itemize}
}}


\end{itemize}

% ------------- PRESENTATIONS -----

%\vspace{-0.55em}
\pagebreak
\section{Presentations}
\begin{itemize}
\item \textit{\textcolor{blue}{Backend Development with Golang}} at Quera's Software Engineering bootcamp (2023)
\item \textit{\textcolor{blue}{Python basics}} at Quera's Software Engineering bootcamp (2023)
\item \textit{\textcolor{blue}{Linux crash course}} at Shahid Beheshti university (2022)
\item \textit{\textcolor{blue}{Intro to Threading}} in Advanced Programming TA class (2022)
\item \textit{\textcolor{blue}{Brief Intro to Functional Programming}} in Khaje-Nasir-Toosi university (2021)
\item \textit{\textcolor{blue}{How to Program in Java}} for junior students (Summer 2020)
\item \textit{\textcolor{blue}{Git crash course}} in Advanced Programming class  (2020)
\item \textit{\textcolor{blue}{Which laptop to buy}} in the First-year students' ceremony (2020)
\item \textit{\textcolor{blue}{Exception Handling best practices}} in Advanced Programming TA class (2020)
\end{itemize}


% ---------- JOBS ---------

\vspace{-0.4em}
\section{Work Experience}
\begin{itemize}

\item \textit{\textcolor{blue}{Software Engineer (Back-End)}} at \href{https://snapp.ir/about}{\textcolor{blue}{Snapp}} -
    Developed microservice-based software enhancing system scalability and reliability  with Go (Sep 2023-current)

\item \textit{\textcolor{blue}{Technical Content Developer}} at \href{https://quera.org}{\textcolor{blue}{Quera}} - Design \textbf{programming challenges} for Go \& Java. Teach Linux \& Python \& Go \& Echo (2021-current)

\item \textit{\textcolor{blue}{Technical Content Developer}} at {\href{https://javacup.ir}{\textcolor{blue}{Javacup}}} - Produce content about Java. \textbf{Held Javacup Exam} twice. (2019-2022)

\item \textit{{\href{https://asta.ir}{\textcolor{blue}{Back-End intern}}}} at Asta. Develop maintainable apps with JAX-RS \& Spring Boot. (Summer 2021)
\end{itemize}

% ---------- SKILLS -------

\vspace{-0.5em}
\section{Skills}
\cvlistitem{Programming Language (Fluent):  Python, Go, C, Java, Bash}
\cvlistitem{Programming Language (Familiar): SQL, JavaScript, Elixir, Haskell, Lua}
\cvlistitem{Frameworks: Echo, Fiber, JAX-RS, Junit}
\cvlistitem{Libraries: Networkx, Numpy, Pandas, Matplotlib, Seaborn, Beautiful Soup, Scikit-learn, PyTorch, Testify}
\cvlistitem{Tools: Linux, Git, Curl, Swagger, Docker, Redis, Prometheus, Graphana, NATS, OpenShift, Make, Maven}


\vspace{-1em}
\section{Languages}
\cvlistitem{Persian: Native}
\cvlistitem{English: Proficient (Academic IELTS: Overall 7.5, Speaking:7.0  Writing:6.0 Listening:8.5 Reading:9.0)}


% ----------- PROJECTS ------------

\vspace{-0.5em}
\section{Key Projects}

\cventry{}{(Test, Debug and Repair Software)}
{\textit{{\href{https://github.com/rsharifnasab/complex-network-fault-localization}{\textcolor{blue}{~Fault Localization with Complex Network techniques}}} }}{Jun-Jul 2023}{}{}
\cvlistitem{\textit{Keywords: Program Slicing, Code Coverage, Fault Localization, Centrality Measures, Complex Network}}


\vspace{-0.3mm}
\cventry{}{(B.Sc Project / Guide: Dr. Vahidi)}
{\textit{{\href{https://github.com/rsharifnasab/DJ}{\textcolor{blue}{~Distributed Code Judge}}}} }{Sept 2021-Aug 2022}{}{}
\cvlistitem{A utility for \textbf{TA}s which helps them judge students' codes more flexibly than traditional judges.}
\cvlistitem{Received the \textbf{best project award} in fall 2022 by SBU's computer faculty.}
\cvlistitem{\textit{Keywords: TA, Automatic Judge, Script, Programming, Source code}}

\vspace{-0.3mm}
\cventry{}{(Computer Networks)}
{\textit{{\href{https://github.com/rsharifnasab/go-linkstate-simulation}{\textcolor{blue}{~Link State Simulation}}} }}{Jun-Jul 2021}{}{}
\cvlistitem{Implementing Manager and Router programs in Go}

\vspace{-0.3mm}
\cventry{}{(Computer Networks)}
{\textit{{\href{https://github.com/rsharifnasab/go-socket-http-server/}{\textcolor{blue}{~Dummy HTTP Server}}} }}{Mar-Apr 2021}{}{}
\cvlistitem{Implementing dummy HTTP server in Go}

\vspace{-0.3mm}
\cventry{}{(Internet Engineering)}
{\textit{{\href{https://github.com/rsharifnasab/java-http-client}{\textcolor{blue}{~Dummy HTTP client}}} }}{Jan 2021}{}{}
\cvlistitem{Implementing a dummy HTTP client in pure Java}

\vspace{-0.3mm}
\cventry{}{(Operating Systems)}
{\textit{{\href{https://github.com/rsharifnasab/os_project}{\textcolor{blue}{~Sleeping Barber}}} }}{Nov 2020}{}{}
\cvlistitem{Sleeping barber Implementation in C}

\vspace{-0.3mm}
\cventry{}{(Compiler Principles)}
{\textit{{\href{https://github.com/rsharifnasab/sbu_compiler}{\textcolor{blue}{~Roulang Compiler}}} }}{Apr-Aug 2020}{}{}
\cvlistitem{Compiling Roulang source code to Java ByteCode with ASM}

\vspace{-0.3mm}
\cventry{}{(Data Structures)}
{\textit{{\href{https://github.com/rsharifnasab/sbu_vi_limited}{\textcolor{blue}{~Vi Clone}}} }}{Jan-Jul 2020}{}{}
\cvlistitem{Simple Vi-like editor with Piece Table and Trie Tree (Java)}


% ------------- AWARDS -------
\vspace{-1em}
\section{Achievements/Awards}

\cvlistitem {Awarded the \textbf{best B.Sc's Thesis-Project} award by SBU’s computer faculty (2022) }
\cvlistitem {Secured 11\textsuperscript{th}/130 in \textbf{National Computer Olympiad}. Participants were top students (By GPA) of top universities in Iran. (2022) }
\cvlistitem{Granted \textbf{merit-based master's scholarship} by Shahid Beheshti University. (2022)}
% \cvlistitem{Qualified for Masters's degree without participating in the entrance exam (Straight M.Sc) for Shahid Beheshti University. (2022)}

\cvlistitem{Secured 8\textsuperscript{th} place in {\href{https://quera.org}{\textcolor{blue}{Quera Connect}}} contest in Go programming language. (2021)   }

\cvlistitem{Secured 14\textsuperscript{th} place in the {\href{https://snapptrip.com}{\textcolor{blue}{Snapptrip}}} internship contest in Java programming language. (2020)}

\cvlistitem{Earned \href{https://hacktoberfest.com/}{\textcolor{blue}{Hacktoberfest}}{} prize for contributing to open-source software}


\cvlistitem{Secured 3\textsuperscript{rd}/190 place in the {\href{https://javacup.ir}{\textcolor{blue}{Javacup}}} contest. Which led to a \textbf{\textit{Java Certified Professional Developer}} certificate. (2019)}


\cvlistitem{Secured 1\textsuperscript{st} place in first-year and second-year students' contest at Shahid Beheshti university. (2018)}

\cvlistitem{Ranked 1101\textsuperscript{th} in the National entrance exam for B.Sc Studies among 120,000 students. (2018)}

\cvlistitem{Reached Semi-final in National Mathematics \& Computer Olympiad.
(2016) }
\cvlistitem{Qualified in the National Organization for Development of Exceptional talents (NODET) entrance exam. (2011)}



\end{document}
